DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-19 paper/appendix.tex
revision
Updates to paper
revision 2

\begin{figure*}[t]
  \centering
  \includegraphics[width=.9\textwidth]{figs/TrainingLoss}
  \caption{Change in loss value throughout training.}
  \label{fig:modelloss}
\end{figure*}

@@

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network are initialized using a Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps. When a model was trained
with the  aformentioned data, the training loss was 0.0188 and the
validation  loss was 0.0132.
The change of the loss value over the course of model training can be
seen in Figure~\ref{fig:modelloss}.

>>>>

\begin{figure*}[h]
  \centering
  \includegraphics[width=.9\textwidth]{figs/TrainingLoss}
  \caption{Change in loss value throughout training.}
  \label{fig:modelloss}
\end{figure*}

@@

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track2} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network are initialized using a Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps. When a model was trained
with the  aformentioned data, the training loss was 0.0188 and the
validation  loss was 0.0132.
The change of the loss value over the course of model training can be
seen in Figure~\ref{fig:modelloss}.

### 2018-04-19 paper/comparison.tex
revision 2

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Jetson TX2 exhibit superior performance when
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 1.33X faster than
the Pi 3, while the TX2 (CPU) and TX2 (GPU) are 2.79X and 4.16X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 33.3 ms 
WCET by a clear margin,
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
and, in the case of the TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that the TX2
(GPU) performance does not change much, as most of the neural network 
computation is done by the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_model}
  \caption{Average control loop execution time when multiple DNN
    models are co-scheduled. }
  \label{fig:sys_model}
\end{figure}

Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 30 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the results suggest that the TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN models we tested.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{figs/compare_benchmark_read}
    \caption{BwRead}
    \label{fig:sys_bench_read}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.4\textwidth}
    \includegraphics[width=\textwidth]{figs/compare_benchmark}
    \caption{BwWrite}
    \label{fig:sys_bench_write}    
  \end{subfigure}
  \caption{Average processing time vs. the number of memory
    memory intensive co-runners.}
  \label{fig:sys_bench}    
\end{figure}

Figure~\ref{fig:sys_bench} shows the results of synthetic memory
intensive task co-scheduling experiment. 
For read co-runners (BwRead), the performance of all platforms
gradually decreased as additional BwRead instances are introduced: up
to 1.6X for Pi 3, up to 1.3X for Intel UP, and up to 1.6X and 2.2X for the TX2
(CPU) and TX2(GPU), respectively.
For write co-runners (BwWrite), however, we observe generally more
noticieable execution time increases. In particular, as we discussed
earlier in Section~\ref{sec:evaluation}, the Pi 3 suffers up to 11.6X
execution time increase. We also observe increased control loop
execution timing in the Intel Up and Jetson TX2, although the degree
of the increase is not as dramatic as the Pi 3.

@@

Another interesting observation is that the TX2 (GPU) also suffers
considerable execution time increase (2.3X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architecture based
platforms where both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, the TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there was no contention between the CPU cores and the GPU.

@@

In summary, we find that todays embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
vision and end-to-end deep learning based real-time control
applications. Furthermore, availability of CPU cores and GPU on these
platforms allow consolidating mutiple deep neural network based AI
workloads. However, shared resource contention among these diverse
computing resources remains an important issue that must be understood
and controlled, especially for safety-critical applications.

>>>>

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used. (cf. Figure~\ref{fig:perf-vs-corecnt})
Both the Intel UP and Jetson TX2 exhibit better performance than
Raspberry Pi 3. When all four CPU cores are used, Intel UP is
1.33X faster than Pi 3, while TX2 (CPU) and TX2 (GPU) are 2.79X and
4.16X times faster, respectively, than Pi 3.
Thus, they all satisfy 33.3 ms WCET by a clear margin, and, in the
case of the TX2, 50 Hz or even 100 Hz real-time control is feasible
with the help of its GPU.
Another observation is that the DNN task's performance on TX2 (GPU)
does not change much as we increase the number of cores. This
isbecause most of the neural network computation is done by the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_model}
  \caption{Timing impact of co-scheduling multiple DNNs on different
    embedded multicore platforms. %% 1Nx1C: one DNN
    %% model using one core; 4Nx1C: four DNN models each using one core;
    %% 1Nx2C: one DNN model using two cores; 2Nx2C: two DNN models each
    %% using two cores.
  }
  \label{fig:sys_model}
\end{figure}

Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment
(cf. Figure~\ref{fig:perf-vs-modelcnt}). Once again, they can comfortably
satisfy 30 Hz real-time performance for all of the co-scheduled DNN control
loops, and in the case of the TX2 (GPU), even 100 Hz real-time control
is feasible in all co-scheduling setups.
Given that the GPU must be shared among the co-scheduled DNN
models, the results suggest that the TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN models we tested.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{figs/compare_benchmark_read}
    \caption{BwRead}
    \label{fig:sys_bench_read}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.45\textwidth}
    \includegraphics[width=\textwidth]{figs/compare_benchmark}
    \caption{BwWrite}
    \label{fig:sys_bench_write}    
  \end{subfigure}
  \caption{Average processing time vs. the number of memory
    memory intensive co-runners.}
  \label{fig:sys_bench}    
\end{figure}

Figure~\ref{fig:sys_bench} shows the results of synthetic memory
intensive task co-scheduling experiment
(cf. Figure~\ref{fig:perf_vs_bandwidth}).
For read co-runners (BwRead), the performance of all platforms
gradually decreased as additional BwRead instances are introduced: up
to 1.6X for Pi 3, up to 1.3X for Intel UP, and up to 1.6X and 2.2X for
the TX2 (CPU) and TX2(GPU), respectively.
For write co-runners (BwWrite), however, we observe generally more
noticieable execution time increases. As we discussed
earlier in Section~\ref{sec:evaluation}, Pi 3 suffers up to 11.6X
execution time increase, while Intel UP and Jetson TX2 suffer less
dramatic but still significant execution time increases.

@@

Another interesting observation is that the TX2 (GPU) also suffers
considerable execution time increase (2.3X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU (i.e., gthe DNN
model has dedicated access to the GPU.) This is, however, a 
known characteristic of integrated CPU-GPU architecture based
platforms in which both CPU and GPU share the same memory
subsystem~\cite{Ali2017} and therefore can suffer bandwidth contention
as we observe in this case.

@@

In summary, we find that todays embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
DNN based real-time control applications. Furthermore, availability of
CPU cores and GPU on these platforms allow consolidating mutiple DNN
workloads. However, shared resource contention among these diverse
computing resources remains an important issue that must be understood
and controlled, especially for safety-critical applications.

### 2018-04-19 paper/conclusion.tex
revision 2

\section{Conclusion}\label{sec:conclusion}
We presented DeepPicar, a low cost autonomous car platform that is
inexpensive to build, but is based on state-of-the-art AI technology:
End-to-end deep learning based real-time control.
Specifically, DeepPicar uses a deep convolutional neural network to
predict steering angles of the car directly from camera input data
in real-time. Importantly, DeepPicar's neural network architecture is
almost identical to that of NVIDIA's real self-driving car.

Despite the complexity of the neural network, DeepPicar uses a
low-cost Raspberry Pi 3 quad-core computer as its sole computing
resource. We systematically analyzed the real-time characteristics of
the Pi 3 platform in the context of deep-learning based real-time
control applications, with a special emphasis on real-time deep neural
network inferencing.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's deep-learning based control system and the impact of
computing hardware architectures.
We find all tested embedded platforms, including the Pi 3, are capable
of supporting deep-learning based real-time control, from 20 Hz up to
100 Hz, depending on the platform and its system
configuration. However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.

>>>>

\section{Conclusion}\label{sec:conclusion}
We presented DeepPicar, a low cost autonomous car platform that is
inexpensive to build, but is based on state-of-the-art AI technology:
End-to-end deep learning based real-time control.
Specifically, DeepPicar uses a deep convolutional neural network to
predict steering angles of the car directly from camera input data
in real-time. Importantly, DeepPicar's neural network architecture is
identical to that of NVIDIA's real self-driving car DAVE-2.

Despite the complexity of the neural network, DeepPicar uses a
low-cost embedded quad-core computer, the Raspberry Pi 3,  as its sole
computing resource.
We systematically analyzed the platform's real-time capability in
supporting the DNN-based real-time control task.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's DNN based control system and the impact of
computing hardware architectures.
We find all tested embedded platforms, including the Pi 3, are capable
of supporting deep-learning based real-time control, from 20 Hz up to
100 Hz, depending on the platform and its system
configuration. Futhermore, all platforms were capable of consolidating
multiple DNN models and/or tasks.

However, when consolidating multiple models/tasks, shared resource
contention remains an important issue that must be considered to
ensure desired real-time performance on these shared memory based
embedded computing platforms. 
Toward this end, we evaluated the impact of shared resource contention
to the DNN workload in diverse consolidated workload setups, and
evaluated the effectivness of state-of-the-art shared resource
isolation mechanisms in protecting real-time performance of the DNN
workload.

### 2018-04-19 paper/evaluation-cachepart.tex
revision 2

Figure \ref{fig:palloc_bandwidth_exectime} shows the
result. For BwRead, when cache partitioning is enabled, DNN
performance becomes slightly better, with a improvement of  
\textasciitilde6.5\%. For BwWrite, cache partitioning actually makes
the DNN performance slightly worse that that of w/o partitioning.

>>>>

Figure \ref{fig:palloc_bandwidth_exectime} shows the
result. Compared to Figure~\ref{fig:perf_vs_bandwidth} where no cache
partioning is applied, assigning a dedicated L2 cache parititon to
each core does not provide significant isolation benefits: For BwRead
co-runners, cache partitioning slightly improves isolation; but for
BwWrite co-runners, cache partitioning causes worse worst-case
slowdown.

### 2018-04-19 paper/evaluation-drampart.tex
revision 2

In this subsection, we examine the DNN workload's memory bandwidth
sensitivity and the effect of memory bandwidth throttling in providing
isolation. For the experiments, we use MemGuard\cite{Yun2013}, which 
can limit the amount of memory bandwidth each core receives. MemGuard
operates periodically, at an 1ms interval, and uses hardware
performance counters to throttle cores if they exceed their given
bandwidth budgets within each regulation period (i.e., 1ms) by
scheduling high-priority idle kernel threads.

In the first experiment, we measure the performance of the DNN model
running on a single core, Core 0, first w/o using MemGuard and then w/
using MemGuard while varying the core's bandwidth throttling parameter
from 500 MB/s down to 100 MB/s.

@@

Figure \ref{fig:memguard_multicore} shows the result. When the DNN
model executing core is throttled at 400 MB/s or more, performance of
the model is largely the same as the non-throttled case. However, as
we decreate the assigned memory badnwdith below 300 MB/s, we start to
observe noticably decreases in the model's performance. In other
words, the DNN model is sensitive to memory bandwidth and that it
requires 400 MB/s or more bandwidth should be given to ensure ideal
performance.

In the next experiment, we again repeat the experiment in
Section~\ref{sec:eval-memhog}---i.e., co-scheduling the DNN model and
three Bandwidth (BwRead or BwWrite) instances---but this time we
throttle the cores that execute the co-runners using MemGuard by 
varying their bandwidth budgets to see ther impact in the DNN model's
performance.

>>>>

In this subsection, we examine the DNN workload's memory bandwidth
sensitivity and the effect of memory bandwidth throttling in providing
isolation. For the experiments, we use MemGuard\cite{Yun2013}, which 
can limit the amount of memory bandwidth each core receives. MemGuard
operates periodically, at an 1ms interval, and uses hardware
performance counters to throttle cores if they exceed their given
bandwidth budgets within each regulation period (i.e., 1ms) by
scheduling high-priority idle kernel threads, until the next period begins.

In the first experiment, we measure the performance of the DNN model
on a single core, first w/o using MemGuard and then w/
using MemGuard while varying the core's bandwidth throttling parameter
from 500 MB/s down to 100 MB/s.

@@

Figure \ref{fig:memguard_multicore} shows the result. When core
executing the DNN model is throttled at 400 MB/s or more, performance
of the model is largely the same as the non-throttled case. However, as
we decrease the assigned memory bandwidth below 300 MB/s, we start to
observe noticeable decreases in the model's performance. In other
words, the DNN model is sensitive to memory bandwidth and that it
requires 400 MB/s or more bandwidth should be given to ensure ideal
performance.

In the next experiment, we again repeat the experiment in
Section~\ref{sec:eval-memhog}---i.e., co-scheduling memory intensive
synthetic tasks---but this time we
throttle the cores of the co-runners using MemGuard and vary their
memory bandwidth budgets to see their impact on the DNN model's 
performance.

### 2018-04-19 paper/evaluation.tex
revision 2

\subsection{Summary of the Findings}
So far, we have evaluated DeepPicar's real-time
characteristics from the perspective of end-to-end deep learning based
real-time control, and made several observations.

First, we find that DeepPicar's computing platform, the Raspberry Pi
3, offers sufficient computing capacity to perform deap-learning based
real-time control at 30 Hz frequency (or 33.3 ms per control
loop). Given the complexity of the DNN used, we were pleasantly
surprised by this finding. 
%% The time breakdown shows that the DNN inferencing operation, 
%% performed by the Tensorflow library, dominates the execution time, 
%% which is expected.

Second, we find that scalability of Tensorflow's DNN 
implementation is limited. We find that using all four cores can double 
performance of the CNN, but compared to using three cores, performance
improvement is relatively minimal.

Third, we find that consolidating multiple DNN models---on different CPU
cores---is feasible as we find: (1) DNN performance using a single
core is not much worse than using multiple cores; (2) multiple DNN
models running simultaneously cause moderate interference.

Fourth, we find that consolidating memory (DRAM) performance
intensive applications (especially write-heavy ones) can jeopadize
the DNN inferencing task's performance even when all tasks have
dedicated cores due to contention in shared hardware resources; we
observe up to 11.6X slowdown.

Lastly, we find that the DNN inferencing workload is not sensitive
to cache space and that cache partitioning is not effective in
providing timing isolation to our DNN workload. On the other hand, we
find that the DNN workload is sensitive to memory bandwidth and that
memory bandwidth throttling is effective in improving performance
isolation.

>>>>

%% \subsection{Summary of the Findings}
%% So far, we have evaluated DeepPicar's real-time
%% characteristics from the perspective of end-to-end deep learning based
%% real-time control, and made several observations.

%% First, we find that DeepPicar's computing platform, the Raspberry Pi
%% 3, offers sufficient computing capacity to perform deap-learning based
%% real-time control at 30 Hz frequency (or 33.3 ms per control
%% loop). Given the complexity of the DNN used, we were pleasantly
%% surprised by this finding. 
%% %% The time breakdown shows that the DNN inferencing operation, 
%% %% performed by the Tensorflow library, dominates the execution time, 
%% %% which is expected.

%% Second, we find that scalability of Tensorflow's DNN 
%% implementation is limited. We find that using all four cores can double 
%% performance of the CNN, but compared to using three cores, performance
%% improvement is relatively minimal.

%% Third, we find that consolidating multiple DNN models---on different CPU
%% cores---is feasible as we find: (1) DNN performance using a single
%% core is not much worse than using multiple cores; (2) multiple DNN
%% models running simultaneously cause moderate interference.

%% Fourth, we find that consolidating memory (DRAM) performance
%% intensive applications (especially write-heavy ones) can jeopadize
%% the DNN inferencing task's performance even when all tasks have
%% dedicated cores due to contention in shared hardware resources; we
%% observe up to 11.6X slowdown.

%% Lastly, we find that the DNN inferencing workload is not sensitive
%% to cache space and that cache partitioning is not effective in
%% providing timing isolation to our DNN workload. On the other hand, we
%% find that the DNN workload is sensitive to memory bandwidth and that
%% memory bandwidth throttling is effective in improving performance
%% isolation.

### 2018-04-19 paper/related.tex
revision 2

There are several relatively inexpensive RC-car based autonomous car
testbeds. MIT's RaceCar~\cite{shin2017project} and UPenn's
F1$/$10~\cite{upennf1tenth} are both based on a Trexx 1/10 scale RC
car and a powerful NVIDIA Jetson computing platform equipped with many
sophisticated sensor packages such as a lidar. However, they both cost
more than \$3,000, requiring considerable
investment. DonkeyCar~\cite{donkeycar} is similar to our DeepPicar as
it also uses a Raspberry Pi 3 and a CNN for end-to-end control,
although it costs slightly more because it uses a more expensive 1/16
scale RC car. The main contribution of our paper is not the hardware
design but in the detailed analysis of computational characteristics
for the CNN-based end-to-end real-time control.

In this paper, we have analyzed real-time performance of a CNN, which
was used in NVIDIA's DAVE-2 self-driving car~\cite{Bojarski2016}, on a 
low-cost raspberry pi 3 quad-core platform. It should be noted,
however, that DAVE-2's CNN is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters, much larger than DAVE-2's CNN.
Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.

@@

While continuing performance improvements in embedded computing
platforms will certainly make processing these complex CNNs faster,
another actively investigated approrach is to reduce the required
computational complexity itself.
When a DNN is deployed in those implementations with limited
resources, such as memory and power, the floating-point operations
involved in the large matrix multiplications are a burdensome task.
Many recent advances in network compression have shown promising results
in reducing such computational cost during the feedforward
process. The fundamental assumption in those techniques is that the
DNNs are redundant in their structure and representation. For example,
network pruning can thin out the network and provides a more condensed
topology~\cite{han2015deep}.
Another common compression method is to reduce the
quantization level of the network parameters, so that arithmetic
defined with the floating-point operations are replaced with low-bit
fixed-point counterparts. To this end, single bit quantization of the
network parameters or ternary quantization have been recently proposed
~\cite{hwang2014fixed,soudry2014expectation,kim2016bitwise,rastegari2016xnor,hubara2016binarized,beauchamp2006embedded,govindu2004analysis}.
In those networks, the inner product between the
originally real-valued parameter vectors is defined with XNOR followed
by bit counting, so that the network can greatly minimize the
computational cost in the hardware implementations. This drastic
quantization can produce some additional performance loss, but those
new binarized or ternarized systems provide a simple quantization
noise injection mechanism during training so that the additional error
is minimized to an acceptable level.

@@

These research efforts are expected to make complex DNNs more
accessible for real-time embedded systems. We plan to investigate the
feasibility of these approaches in the context of DeepPicar so that we
can use even more resource constrained micro-controller class
computing platforms instead of Raspberry Pi3.

>>>>

There are several relatively inexpensive RC-car based autonomous car
testbeds. MIT's RaceCar~\cite{shin2017project} and UPenn's
F1$/$10~\cite{upennf1tenth} are both based on a Trexx 1/10 scale RC
car and a powerful NVIDIA Jetson multicore computing platform, which
is equipped with many sophisticated sensor packages such as a lidar.
However, they both cost more than \$3,000, requiring considerable
investment. DonkeyCar~\cite{donkeycar} is similar to our DeepPicar as
it also uses a Raspberry Pi 3 and a similar CNN for end-to-end
control, although it costs more (about \$200).
%% because it uses a more
%% expensive 1/16 scale RC car than our 1/24 scale one.
The main contribution of our paper is in the detailed analysis of
computational aspects of executing a CNN-based real-time control
workload on diverse embedded computing platforms.

In this paper, we have analyzed real-time performance of a real-world
CNN, which was used in NVIDIA's DAVE-2 self-driving
car~\cite{Bojarski2016}, on a low-cost raspberry pi 3 quad-core 
platform and other embedded multicore platforms. It should be noted, 
however, that DAVE-2's CNN is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters, much larger than DAVE-2's CNN.
Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.

@@

While continuing performance improvements in embedded computing
platforms will certainly make processing these complex CNNs faster,
another actively investigated approrach is to reduce the required
computational complexity itself.
%% When a DNN is deployed in those implementations with limited
%% resources, such as memory and power, the floating-point operations
%% involved in the large matrix multiplications are a burdensome task.
Many recent advances in network compression have shown promising results
in reducing such computational cost during the feedforward
process. The fundamental assumption in those techniques is that the
DNNs are redundant in their structure and representation. For example,
network pruning can thin out the network and provides a more condensed
topology~\cite{han2015deep}.

Another common compression method is to reduce the
quantization level of the network parameters, so that arithmetic
defined with the floating-point operations are replaced with low-bit
fixed-point counterparts. To this end, single bit quantization of the
network parameters or ternary quantization have been recently proposed
~\cite{hwang2014fixed,soudry2014expectation,kim2016bitwise,rastegari2016xnor,hubara2016binarized,beauchamp2006embedded,govindu2004analysis}.
In those networks, the inner product between the
originally real-valued parameter vectors is defined with XNOR followed
by bit counting, so that the network can greatly minimize the
computational cost in the hardware implementations. This drastic
quantization can produce some additional performance loss, but those
new binarized or ternarized systems provide a simple quantization
noise injection mechanism during training so that the additional error
is minimized to an acceptable level.

@@

These research efforts are expected to make complex DNNs more
accessible for a wider range of real-time embedded systems. We plan to
investigate the feasibility of these approaches in the context of
DeepPicar so that we can use even more resource constrained
micro-controller class computing platforms.
